Quality measure notes

### 2021-08-10 StateOfPractice/Ao-Report/11Introduction.tex
MI report - updated research question format

\begin{enumerate}
\item What are the pain points for developers working on MI software projects? What solutions the developers have tried to address the pain points?
\item What artifacts the projects generated?
\item What role does documentation play in the projects? What are the developers' attitudes toward it?
\item What principles, processes, methodologies, and tools the projects used?
\item What is the current status of the following software qualities for the projects? What actions have the developers taken to address them?
\begin{itemize}
	\item Installability
	\item Correctness \& Verifiability
	\item Reliability
	\item Robustness
	\item Usability
	\item Maintainability
	\item Reusability
	\item Understandability
	\item Visibility/Transparency
	\item Reproducibility
\end{itemize}
\item How does the software quality ranking generated by our methods compare with the ratings from the community?
\end{enumerate}

>>>>

\begin{description}
\item[RQ1.] What are the pain points for developers working on MI software projects? What solutions the developers have tried to address the pain points?
\item[RQ2.] What artifacts the projects generated?
\item[RQ3.] What role does documentation play in the projects? What are the developers' attitudes toward it?
\item[RQ4.] What principles, processes, methodologies, and tools the projects used?
\item[RQ5.] What is the current status of the following software qualities for the projects? What actions have the developers taken to address them?
\begin{itemize}
	\item Installability
	\item Correctness \& Verifiability
	\item Reliability
	\item Robustness
	\item Usability
	\item Maintainability
	\item Reusability
	\item Understandability
	\item Visibility/Transparency
	\item Reproducibility
\end{itemize}
\item[RQ6.] How does the software quality ranking generated by our methods compare with the ratings from the community?
\end{description}

### 2021-08-10 StateOfPractice/Ao-Report/16AnswersToResearchQuestions.tex
MI report - updated research question format

\section{Pain Points and Solutions}
\label{sec_rq1_pain_points}
\textit{RQ1. What are the pain points for developers working on MI software projects? What solutions have the developers tried to address the pain points?}

@@

\section{Artifacts in the Projects}
\label{sec_rq2_artifacts}
\textit{RQ2. What artifacts the projects generated?}

@@

\section{Documentation in the Projects}
\label{sec_rq3_documentation}
\textit{RQ3. What role does documentation play in the projects? What are the developers' attitudes toward it?}

@@

\section{Principles, Processes, Methodologies, and Tools in the Projects}
\label{sec_rq4_PPMT}
\textit{RQ4. What principles, processes, methodologies, and tools the projects used?}

@@

\section{Software Qualities}
\label{sec_rq5_qualities}
\textit{RQ5. What is the current status of the following software qualities for the projects? What actions have the developers taken to address them?}

@@

\section{Our Ranking versus the Community Ratings}
\label{sec_rq6_comparison}
\textit{RQ6. How does the software quality ranking generated by our methods compare with the ratings from the community?}

>>>>

\section{Pain Points and Solutions}
\label{sec_rq1_pain_points}
\begin{description}\item[RQ1.] What are the pain points for developers working on MI software projects? What solutions have the developers tried to address the pain points?\end{description}

@@

\section{Artifacts in the Projects}
\label{sec_rq2_artifacts}
\begin{description}\item[RQ2.] What artifacts the projects generated?\end{description}

@@

\section{Documentation in the Projects}
\label{sec_rq3_documentation}
\begin{description}\item[RQ3.] What role does documentation play in the projects? What are the developers' attitudes toward it?\end{description}

@@

\section{Principles, Processes, Methodologies, and Tools in the Projects}
\label{sec_rq4_PPMT}
\begin{description}\item[RQ4.] What principles, processes, methodologies, and tools the projects used?\end{description}

@@

\section{Software Qualities}
\label{sec_rq5_qualities}
\begin{description}\item[RQ5.] What is the current status of the following software qualities for the projects? What actions have the developers taken to address them?\end{description}

@@

\section{Our Ranking versus the Community Ratings}
\label{sec_rq6_comparison}
\begin{description}\item[RQ6.] How does the software quality ranking generated by our methods compare with the ratings from the community?\end{description}
